---
title: "Code for 'FDA in Biomechanics'"
output: github_document
author: Edward Gunning
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

This repository contains `R` code for the manuscript 'FDA in Biomechanics'.

## Notes

* For all chapters, standard `.R` scripts to reproduce each figure are contained in a separate folder:
  * :open_file_folder: [**Chapter 1**](chapter-01/)
  * :open_file_folder: [**Chapter 2**](chapter-02/)
  * :open_file_folder: [**Chapter 3**](chapter-03/)
  * :open_file_folder: [**Chapter 4**](chapter-04/)
  * :open_file_folder: [**Chapter 5**](chapter-05/)
  * :open_file_folder: [**Case Study**](chapter-06/)

* For the **'Case Study'** chapter, _**Quarto**_ (and `.RMD`) notebooks that document the case study analysis in a step-by-step fashion are also provided:
  * 📔 [**Part 1** - Data Import and Exploration](chapter-06/Case-Study-Part-01-MD.md)
  * 📔 [**Part 2** - Analysis of Healthy Controls](chapter-06/Case-Study-Part-02-MD.md)
  * 📔 [**Part 3** - Analysis of Impaired Movement](chapter-06/Case-Study-Part-03-MD.md)

# Data

The data used in the review are all publicly available.

 1. **The Childrens' Gait Data Set** can be accessed directly from the `fda` \textsf{R} package:

```{r, fig.asp=0.5, fig.width=8, message=FALSE, warning=FALSE, fig.align='center'}
library(fda)
data("gait")
gaittime <- as.numeric(rownames(gait))
par(mfrow = c(1, 2))
matplot(x = gaittime,
        y = gait[,,1],
        type = "b",
        pch = 20, 
        lty = 1, 
        cex = 0.75,
        xlab = "Normalised Time",
        ylab = "Angle (°)",
        main = "Hip")
grid(lty = 1)
matplot(x = gaittime,
        y = gait[,,2],
        type = "b",
        pch = 20, 
        cex = 0.75,
        lty = 1, 
        xlab = "Normalised Time",
        ylab = "Angle (°)",
        main = "Knee")
grid(lty = 1)
```

2. **The Juggling Data** were initially downloaded from (https://archive.mbi.ohio-state.edu/vod/mbi-media/e-162/1400789954_juggling.zip) but the link is no longer working. <span style="color: red;">Note: Pending Permission from Prof. Jim Ramsay</span>. Therefore, we have uploaded a copy of the data to :open_file_folder: [**chapter-02/juggling-data/**](chapter-02/juggling-data/), which can be accessed from within this repository as follows:

```{r, fig.asp = 1, fig.width=8, message=FALSE, warning=FALSE, fig.align='center'}
x <- readr::read_table2("chapter-02/juggling-data/Xcoord.txt", col_names = FALSE) # x coordinates
y <- readr::read_table2("chapter-02/juggling-data//Ycoord.txt", col_names = FALSE) # y coordinates
z <- readr::read_table2("chapter-02/juggling-data//Zcoord.txt", col_names = FALSE) # z co-ordinates

cols <- rainbow(ncol(x)) 
t <- (0:(nrow(x)-1)) * 5 # time arguments (approx. ms)
par(mfrow = c(3, 1))
matplot(t, as.matrix(x), type = "l", lty = 1, xlab = expression(t), ylab = expression(x(t)), col = cols)
grid(lty = 1)
title(expression(x(t)))
matplot(t, as.matrix(y), type = "l", lty = 1, xlab = expression(t), ylab = expression(y(t)), col = cols)
grid(lty = 1)
title(expression(y(t)))
matplot(t, as.matrix(z), type = "l", lty = 1, xlab = expression(t), ylab = expression(z(t)), col = cols)
grid(lty = 1)
title(expression(z(t)))
```

3. **The GaitRec Data Set** is available for download at https://doi.org/10.6084/m9.figshare.c.4788012.v1. We have written a `.R` script to import, wrangle and store the subset of the data used in the review in [📄 here](chapter-06/01-data-import-and-wrangling.R). 

```{r, fig.asp=0.4, fig.align='center', fig.width=10}
# from the stored copy:
gaitrec <- readRDS("chapter-06/data/GRF_dataset_PRO_meta.rds")

# split into three force components:
v <- as.matrix(gaitrec[gaitrec$component == "vertical", paste0("time_", 0:100)])
ap <- as.matrix(gaitrec[gaitrec$component == "anterior_posterior", paste0("time_", 0:100)])
ml <- as.matrix(gaitrec[gaitrec$component == "medio_lateral", paste0("time_", 0:100)])

# plot first 10 obs.:
par(mfrow = c(1, 3))
matplot(x = 0:100,
        y = t(v[1:10,]),
        type = "l",
        lty = 1,
        xlab = "Normalised Time (% of Stance)", 
        ylab = "Force (BW)")
grid(lty = 1)
title("Vertical")
matplot(x = 0:100,
        y = t(ap[1:10,]),
        type = "l", 
        lty = 1, 
        xlab = "Normalised Time (% of Stance)",
        ylab = "Force (BW)")
grid(lty = 1)
title("Anterior-Posterior")
matplot(x = 0:100,
        y = t(ml[1:10,]), 
        type = "l", 
        lty = 1, 
        xlab = "Normalised Time (% of Stance)",
        ylab = "Force (BW)")
grid(lty = 1)
title("Medio-Lateral")
```


# Packages

We primarily use the `fda` (Ramsay, Hooker and Graves, 2020) and `refund` (Goldsmith et al., 202) `R` packages to fit functional data analysis models to biomechanical data.

These extensive software packages have full, dedicated textbooks on how to use them:

* `fda`: Ramsay, Hooker and Graves (2009)

* `refund`: Crainiceanu, Goldsmith, Leroux and Cui (2024) (just released)

These texts, along with the reference manuals for the packages, as great places to learn about the full functionality of the packages.

# `tikzDevice`

We use the [`tikzDevice` package](https://cran.r-project.org/web/packages/tikzDevice/index.html) to produce figure outputs in $\LaTeX$ (e.g., fonts and math symbols). If you are not interested in producing the `.pdf` plots with latex font, then calls such as `tikz(...)` can be ignored.

# References

## Childrens' Gait Data

* Olshen, R. A., Biden, E. N., Wyatt, M. P., & Sutherland, D. H. (1989). Gait Analysis and the Bootstrap. The Annals of Statistics, 17(4), 1419–1440. JSTOR.

* Rice, J. A., & Silverman, B. W. (1991). Estimating the Mean and Covariance Structure Nonparametrically When the Data are Curves. Journal of the Royal Statistical Society. Series B (Methodological), 53(1), 233–243. JSTOR.

* Leurgans, S. E., Moyeed, R. A., & Silverman, B. W. (1993). Canonical Correlation Analysis when the Data are Curves. Journal of the Royal Statistical Society. Series B (Methodological), 55(3), 725–740. JSTOR.

* Ramsay, J. O., & Silverman, B. W. (2005). Functional Data Analysis (2nd ed.). Springer-Verlag. https://doi.org/10.1007/b98888

* Ramsay, J. O., Graves, S., & Hooker, G. (2020). `fda`: Functional Data Analysis. R package version 5.5.1. https://CRAN.R-project.org/package=fda

## Juggling Data

* Ramsay, J. O., Gribble, P., & Kurtek, S. (2014). Description and processing of functional data arising from juggling trajectories. Electronic Journal of Statistics, 8(2), 1811–1816. https://doi.org/10.1214/14-EJS937

* Ramsay, J. O. (2014). Functional data analysis of juggling trajectories: Rejoinder. Electronic Journal of Statistics, 8(2), 1874–1878. https://doi.org/10.1214/14-EJS937REJ

* Ramsay, J. O., Gribble, P., & Kurtek, S. (2014). Analysis of juggling data: Landmark and continuous registration of juggling trajectories. Electronic Journal of Statistics, 8(2), 1835–1841. https://doi.org/10.1214/14-EJS937C

## GaitRec

* Horsak, B., Slijepcevic, D., Raberger, A.-M., Schwab, C., Worisch, M., & Zeppelzauer, M. (2020). GaitRec, a large-scale ground reaction force dataset of healthy and impaired gait. Scientific Data, 7(1), Article 1. https://doi.org/10.1038/s41597-020-0481-z

* Publicly Available Data-Sharing Repository: https://doi.org:10.6084/m9.figshare.c.4788012.v1

## Edward Gunning's Ph.D. Thesis

* The examples in this review were initially developed for Edward Gunning's Ph.D. thesis. The corresponding `GitHub` repository that was released is hosted at [https://github.com/FAST-ULxNUIG/thesis-chapt-1-2](https://github.com/FAST-ULxNUIG/thesis-chapt-1-2)

## `tikzDevice`

* Sharpsteen, C., Bracken, C., Müller, K., Xie, Y., Stubner, R., & Bellack, N. (2023). R package ‘tikzDevice’ [https://github.com/daqana/tikzDevice](https://github.com/daqana/tikzDevice).

## `refund`

* Goldsmith, J., Scheipl, F., Huang, L., Wrobel, J., Di, C.-Z., Gellar, J., Harezlak, J., McLean, M. W., Swihart, B., Xiao, L., Crainiceanu, C. M., Reiss, P. T., Chen, Y., Greven, S., Huo, L., Kundu, M. G., Park, S. Y., Miller, D. L., & Staicu, A.-M. (2020). `refund`: Regression with Functional Data (0.1-23) [Sp-ES]. https://CRAN.R-project.org/package=refund

* Crainiceanu, C. M., Goldsmith, J., Leroux, A., & Cui, E. (2024). Functional Data Analysis with R (1st edition). Chapman and Hall/CRC.


# Session Information (Reproducibility)

```{r}
sessionInfo()
```


